Towards a probability measure approach for Differential Privacy in Bayesian inference

### 2018-07-18 main-sketch.tex
final pass
fninish the todo in red

\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
independent variables --or a combination thereof.
The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
is also drawn to give a rough guide to the significance of difference of medians;
The whiskers extend from the box to show the range of the data. 
A blue box in the plots represents the exponential mechanism behaviour,
while the yellow box next to it represents the performance of a variation of the
basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
The variation considered performs a post processing on the released parameters so that they
are consistent. For instance in the case \todo{more info about the truncation}.
\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

@@

These results although very motivating, are still not enough for real world applications.
Hence, we will continue our work in the follwoing directions:
\begin{enumerate}
  \item For now, we just have a intuitive idea on the accuracy
    behavior of our mechanisms, and not a precise formula or bound on it.
    When do our mechanisms perform better than the baseline mechanism and when they don't?
    How much influence will elements in Section \ref{sec_experiment} have on the
    accuracy? Are there any other important factors we missed? These are
    all questions w.r.t. the accuracy that we are going to explore next, and in a more
    principled and formal way.
\item  Theorem \ref{thm:privacy} provides an upper bound to the  privacy loss for
  $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one.
  Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$.
  This means that we could improve accuracy, by adding less noise --
  that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
\item The choice of the Hellinger distance might seem quite ad-hoc. Hence,
  it is worth exploring other distances over distributions. An interesting class
  of probability metrics is the family of  $f$-divergences \todo{\cite{??}}.
\end{enumerate}

>>>>

\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
independent variables --or a combination thereof.
The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
is also drawn to give a rough guide to the significance of difference of medians;
The whiskers extend from the box to show the range of the data. 
A blue box in the plots represents the exponential mechanism behaviour,
while the yellow box next to it represents the performance of a variation of the
basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
The variation considered performs a post processing on the released parameters so that they
are consistent. For instance in the case when noise is greater than $n$ we will truncate to $n$ to rule out invalid values.
\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

@@

These results although very motivating, are still not enough for real world applications.
Hence, we will continue our work in the follwoing directions:
\begin{enumerate}
  \item For now, we just have a intuitive idea on the accuracy
    behavior of our mechanisms, and not a precise formula or bound on it.
    When do our mechanisms perform better than the baseline mechanism and when they don't?
    How much influence will elements in Section \ref{sec_experiment} have on the
    accuracy? Are there any other important factors we missed? These are
    all questions w.r.t. the accuracy that we are going to explore next, and in a more
    principled and formal way.
\item  Theorem \ref{thm:privacy} provides an upper bound to the  privacy loss for
  $\hexpmech$ and $\hexpmechd$ but  not necessarily a tight one.
  Indeed, experiments have shown that the actual privacy loss in the experiments can be smaller than $\epsilon$.
  This means that we could improve accuracy, by adding less noise --
  that is noise proportional to a higher value of $\epsilon$-- but still achieve $(\epsilon, \delta)$-dp.
\item The choice of the Hellinger distance might seem quite ad-hoc. Hence,
  it is worth exploring other distances over distributions. An interesting class
  of probability metrics is the family of  $f$-divergences \cite{CIT-004}.
\end{enumerate}
